### 2023-03-29 response-to-audit-report.md

 instance Eq Contract where
     {-# INLINABLE (==) #-}
     Close == Close = True
+    Close == _ = False
     Pay acc1 payee1 tok1 value1 cont1 == Pay acc2 payee2 tok2 value2 cont2 =
         acc1 == acc2 && payee1 == payee2 && tok1 == tok2 && value1 == value2 && cont1 == cont2
+    Pay{} == _ = False
     If obs1 cont1 cont2 == If obs2 cont3 cont4 =
         obs1 == obs2 && cont1 == cont3 && cont2 == cont4
-    When cases1 timeout1 cont1 == When cases2 timeout2 cont2 =
+    If{} == _ = False
+    When cases1 timeout1 cont1 == When cases2 timeout2 cont2 =  -- The sequences of tests are ordered for efficiency.
         timeout1 == timeout2 && cont1 == cont2
         && length cases1 == length cases2
         && and (zipWith (==) cases1 cases2)
+    When{} == _ = False
     Let valId1 val1 cont1 == Let valId2 val2 cont2 =
         valId1 == valId2 && val1 == val2 && cont1 == cont2
+    Let{} == _ = False
     Assert obs1 cont1 == Assert obs2 cont2 = obs1 == obs2 && cont1 == cont2
-    _ == _ = False
+    Assert{}  == _ = False

 instance Eq State where
diff --git a/marlowe/src/Language/Marlowe/Scripts.hs b/marlowe/src/Language/Marlowe/Scripts.hs
index 6027202b5..aa397d5fa 100644
--- a/marlowe/src/Language/Marlowe/Scripts.hs
+++ b/marlowe/src/Language/Marlowe/Scripts.hs
@@ -47,7 +47,9 @@ module Language.Marlowe.Scripts
   , alternateMarloweValidator
   , alternateMarloweValidatorHash
   , marloweValidator
+  , marloweValidatorCompiled
   , marloweValidatorHash
+  , mkMarloweValidator
     -- * Payout Validator
   , TypedRolePayoutValidator
   , rolePayoutValidator
@@ -61,8 +63,9 @@ import GHC.Generics (Generic)
 import Language.Marlowe.Core.V1.Semantics as Semantics
 import Language.Marlowe.Core.V1.Semantics.Types as Semantics
 import Language.Marlowe.Pretty (Pretty(..))
+import Ledger.Typed.Scripts (unsafeMkTypedValidator)
 import qualified Plutus.Script.Utils.Typed as Scripts
-import Plutus.Script.Utils.V2.Typed.Scripts (mkTypedValidator, mkUntypedValidator)
+import Plutus.Script.Utils.V2.Typed.Scripts (mkTypedValidator)
 import qualified Plutus.Script.Utils.V2.Typed.Scripts as Scripts
 import qualified Plutus.V1.Ledger.Address as Address (scriptHashAddress)
 import qualified Plutus.V1.Ledger.Value as Val
@@ -92,11 +95,22 @@ import PlutusTx (makeIsDataIndexed, makeLift)
 import qualified PlutusTx
 import qualified PlutusTx.AssocMap as AssocMap
 import PlutusTx.Plugin ()
-import PlutusTx.Prelude as PlutusTxPrelude
+import PlutusTx.Prelude as PlutusTxPrelude hiding (traceError, traceIfFalse)
 import qualified Prelude as Haskell
 import Unsafe.Coerce (unsafeCoerce)

+-- Suppress traces, in order to save bytes.
+
+{-# INLINABLE traceError #-}
+traceError :: BuiltinString -> a
+traceError _ = error ()
+
+{-# INLINABLE traceIfFalse #-}
+traceIfFalse :: BuiltinString -> a -> a
+traceIfFalse _ = id
+
+
 -- | Input to a Marlowe transaction.
 type MarloweInput = [MarloweTxInput]

@@ -136,7 +150,7 @@ rolePayoutValidator = mkTypedValidator @TypedRolePayoutValidator
   $$(PlutusTx.compile [|| mkRolePayoutValidator ||])
   $$(PlutusTx.compile [|| wrap ||])
   where
-    wrap = Scripts.mkUntypedValidator @(CurrencySymbol, TokenName) @()
+    wrap = Scripts.mkUntypedValidator @_ @(CurrencySymbol, TokenName) @()

 {-# INLINABLE rolePayoutValidator #-}
@@ -147,7 +161,7 @@ mkRolePayoutValidator :: (CurrencySymbol, TokenName)  -- ^ The datum is the curr
                       -> Bool                         -- ^ Whether the transaction validated.
 mkRolePayoutValidator (currency, role) _ ctx =
     -- The role token for the correct currency must be present.
-    -- [Marlowe-Cardano Specification: "16. Payment authorized".]
+    -- [Marlowe-Cardano Specification: "17. Payment authorized".]
     Val.singleton currency role 1 `Val.leq` valueSpent (scriptContextTxInfo ctx)

@@ -188,12 +202,10 @@ mkMarloweValidator
             case closeInterval $ txInfoValidRange scriptContextTxInfo of
                 Just interval' -> interval'
                 Nothing        -> traceError "a"
-    -- The incoming balance of each account must be positive.
-    -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
-    let positiveBalances = traceIfFalse "b" $ validateBalances marloweState

     -- Find Contract continuation in TxInfo datums by hash or fail with error.
     let inputs = fmap marloweTxInputToInput marloweTxInputs
+
     {-  We do not check that a transaction contains exact input payments.
         We only require an evidence from a party, e.g. a signature for PubKey party,
         or a spend of a 'party role' token.  This gives huge flexibility by allowing
@@ -201,22 +213,19 @@ mkMarloweValidator
         Then, we check scriptOutput to be correct.
      -}
     let inputContents = fmap getInputContent inputs
+
     -- Check that the required signatures and role tokens are present.
     -- [Marlowe-Cardano Specification: "Constraint 14. Inputs authorized".]
-    let inputsOk = validateInputs inputContents
-
-    -- Since individual balances were validated to be positive,
-    -- the total balance is also positive.
-    let inputBalance = totalBalance (accounts marloweState)
+    let inputsOk = allInputsAreAuthorized inputContents

     -- [Marlowe-Cardano Specification: "Constraint 5. Input value from script".]
-    -- The total incoming balance must match the actual script value being spent.
-    let balancesOk = traceIfFalse "v" $ inputBalance == scriptInValue
-
-    let preconditionsOk = positiveBalances && balancesOk
+    -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+    -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+    -- Check that the initial state obeys the Semantic's invariants.
+    let preconditionsOk = checkState "i" scriptInValue marloweState

-    -- Package the inputs to be applied in the semantics.
     -- [Marlowe-Cardano Specification: "Constraint 0. Input to semantics".]
+    -- Package the inputs to be applied in the semantics.
     let txInput = TransactionInput {
             txInterval = interval,
             txInputs = inputs }
@@ -246,16 +255,25 @@ mkMarloweValidator

                 checkContinuation = case txOutContract of
                     -- [Marlowe-Cardano Specification: "Constraint 4. No output to script on close".]
-                    Close -> traceIfFalse "c" checkScriptOutputAny
+                    Close -> traceIfFalse "c" hasNoOutputToOwnScript
                     _ -> let
                         totalIncome = foldMap collectDeposits inputContents
                         totalPayouts = foldMap snd payoutsByParty
-                        finalBalance = inputBalance + totalIncome - totalPayouts
-                        -- The total account balance must be paid to a single output to the script.
-                        -- [Marlowe-Cardano Specification: "Constraint 3. Single Marlowe output".]
-                        -- [Marlowe-Cardano Specification: "Constraint 6. Output value to script."]
-                        in checkOwnOutputConstraint marloweData finalBalance
+                        finalBalance = scriptInValue + totalIncome - totalPayouts
+                        in
+                             -- [Marlowe-Cardano Specification: "Constraint 3. Single Marlowe output".]
+                             -- [Marlowe-Cardano Specification: "Constraint 6. Output value to script."]
+                             -- Check that the single Marlowe output has the correct datum and value.
+                             checkOwnOutputConstraint marloweData finalBalance
+                             -- [Marlowe-Cardano Specification: "Constraint 18. Final balance."]
+                             -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+                             -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+                             -- Check that the final state obeys the Semantic's invariants.
+                          && checkState "o" finalBalance txOutState
             preconditionsOk && inputsOk && payoutsOk && checkContinuation
+              -- [Marlowe-Cardano Specification: "20. Single satsifaction".]
+              -- Either there must be no payouts, or there must be no other validators.
+              && traceIfFalse "z" (null payoutsByParty || noOthers)
         Error TEAmbiguousTimeIntervalError -> traceError "i"
         Error TEApplyNoMatchError -> traceError "n"
         Error (TEIntervalError (InvalidInterval _)) -> traceError "j"
@@ -274,24 +292,73 @@ mkMarloweValidator
         find (\TxInInfo{txInInfoOutRef} -> txInInfoOutRef == txOutRef) txInfoInputs
     findOwnInput _ = Nothing

-    -- The inputs being spent by this script.
     -- [Marlowe-Cardano Specification: "2. Single Marlowe script input".]
+    -- The inputs being spent by this script, and whether other validators are present.
     ownInput :: TxInInfo
-    ownInput@TxInInfo{txInInfoResolved=TxOut{txOutAddress=ownAddress}} =
+    noOthers :: Bool
+    (ownInput@TxInInfo{txInInfoResolved=TxOut{txOutAddress=ownAddress}}, noOthers) =
         case findOwnInput ctx of
-            Just ownTxInInfo ->
-                case filter (sameValidatorHash ownTxInInfo) (txInfoInputs scriptContextTxInfo) of
-                    [i] -> i
-                    _   -> traceError "w" -- Multiple Marlowe contract inputs with the same address are forbidden.
+            Just ownTxInInfo -> examineScripts (sameValidatorHash ownTxInInfo) Nothing True (txInfoInputs scriptContextTxInfo)
             _ -> traceError "x" -- Input to be validated was not found.

+    -- Check for the presence of multiple Marlowe validators or other Plutus validators.
+    examineScripts
+      :: (ValidatorHash -> Bool)  -- Test for this validator.
+      -> Maybe TxInInfo           -- The input for this validator, if found so far.
+      -> Bool                     -- Whether no other validator has been found so far.
+      -> [TxInInfo]               -- The inputs remaining to be examined.
+      -> (TxInInfo, Bool)         -- The input for this validator and whehter no other validators are present.
+    -- This validator has not been found.
+    examineScripts _ Nothing _ [] = traceError "x"
+    -- This validator has been found, and other validators may have been found.
+    examineScripts _ (Just self) noOthers [] = (self, noOthers)
+    -- Found both this validator and another script, so we short-cut.
+    examineScripts _ (Just self) False _ = (self, False)
+     -- Found one script.
+    examineScripts f mSelf noOthers (tx@TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh) _}} : txs)
+      -- The script is this validator.
+      | f vh = case mSelf of
+                 -- We hadn't found it before, so we save it in `mSelf`.
+                 Nothing -> examineScripts f (Just tx) noOthers txs
+                 -- We already had found this validator before
+                 Just _ -> traceError "w"
+      -- The script is something else, so we set `noOther` to `False`.
+      | otherwise = examineScripts f mSelf False txs
+    -- An input without a validator is encountered.
+    examineScripts f self others (_ : txs) = examineScripts f self others txs
+
     -- Check if inputs are being spent from the same script.
-    sameValidatorHash:: TxInInfo -> TxInInfo -> Bool
-    sameValidatorHash
-        TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh1) _}}
-        TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh2) _}} = vh1 == vh2
+    sameValidatorHash:: TxInInfo -> ValidatorHash -> Bool
+    sameValidatorHash TxInInfo{txInInfoResolved=TxOut{txOutAddress=Ledger.Address (ScriptCredential vh1) _}} vh2 = vh1 == vh2
     sameValidatorHash _ _ = False

+    -- Check a state for the correct value, positive accounts, and no duplicates.
+    checkState :: BuiltinString -> Val.Value -> State -> Bool
+    checkState tag expected State{..} =
+      let
+        positiveBalance :: (a, Integer) -> Bool
+        positiveBalance (_, balance) = balance > 0
+        noDuplicates :: Eq k => AssocMap.Map k v -> Bool
+        noDuplicates am =
+          let
+            test [] = True           -- An empty list has no duplicates.
+            test (x : xs)            -- Look for a duplicate of the head in the tail.
+              | elem x xs = False    -- A duplicate is present.
+              | otherwise = test xs  -- Continue searching for a duplicate.
+          in
+            test $ AssocMap.keys am
+      in
+           -- [Marlowe-Cardano Specification: "Constraint 5. Input value from script".]
+           -- and/or
+           -- [Marlowe-Cardano Specification: "Constraint 18. Final balance."]
+           traceIfFalse ("v"  <> tag) (totalBalance accounts == expected)
+           -- [Marlowe-Cardano Specification: "Constraint 13. Positive balances".]
+        && traceIfFalse ("b"  <> tag) (all positiveBalance $ AssocMap.toList accounts)
+           -- [Marlowe-Cardano Specification: "Constraint 19. No duplicates".]
+        && traceIfFalse ("ea" <> tag) (noDuplicates accounts)
+        && traceIfFalse ("ec" <> tag) (noDuplicates choices)
+        && traceIfFalse ("eb" <> tag) (noDuplicates boundValues)
+
     -- Look up the Datum hash for specific data.
     findDatumHash' :: PlutusTx.ToData o => o -> Maybe DatumHash
     findDatumHash' datum = findDatumHash (Datum $ PlutusTx.toBuiltinData datum) scriptContextTxInfo
@@ -301,7 +368,7 @@ mkMarloweValidator
     checkOwnOutputConstraint ocDatum ocValue =
         let hsh = findDatumHash' ocDatum
         in traceIfFalse "d" -- "Output constraint"
-        $ checkScriptOutput ownAddress hsh ocValue getContinuingOutput
+        $ checkScriptOutput (==) ownAddress hsh ocValue getContinuingOutput

     getContinuingOutput :: TxOut
     getContinuingOutput = case filter (\TxOut{txOutAddress} -> ownAddress == txOutAddress) allOutputs of
@@ -309,20 +376,14 @@ mkMarloweValidator
         _     -> traceError "o" -- No continuation or multiple Marlowe contract outputs is forbidden.

     -- Check that address, value, and datum match the specified.
-    checkScriptOutput :: Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
-    checkScriptOutput addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
-                    txOutValue == value && hsh == Just svh && txOutAddress == addr
-    checkScriptOutput _ _ _ _ = False
-
-    -- Check that address and datum match the specified, and that value is at least that required.
-    checkScriptOutputRelaxed :: Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
-    checkScriptOutputRelaxed addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
-                    txOutValue `Val.geq` value && hsh == Just svh && txOutAddress == addr
-    checkScriptOutputRelaxed _ _ _ _ = False
+    checkScriptOutput :: (Val.Value -> Val.Value -> Bool) -> Ledger.Address -> Maybe DatumHash -> Val.Value -> TxOut -> Bool
+    checkScriptOutput comparison addr hsh value TxOut{txOutAddress, txOutValue, txOutDatum=OutputDatumHash svh} =
+                    txOutValue `comparison` value && hsh == Just svh && txOutAddress == addr
+    checkScriptOutput _ _ _ _ _ = False

     -- Check for any output to the script address.
-    checkScriptOutputAny :: Bool
-    checkScriptOutputAny = all ((/= ownAddress) . txOutAddress) allOutputs
+    hasNoOutputToOwnScript :: Bool
+    hasNoOutputToOwnScript = all ((/= ownAddress) . txOutAddress) allOutputs

     -- All of the script outputs.
     allOutputs :: [TxOut]
@@ -339,8 +400,8 @@ mkMarloweValidator
     marloweTxInputToInput (Input input) = NormalInput input

     -- Check that inputs are authorized.
-    validateInputs :: [InputContent] -> Bool
-    validateInputs = all validateInputWitness
+    allInputsAreAuthorized :: [InputContent] -> Bool
+    allInputsAreAuthorized = all validateInputWitness
       where
         validateInputWitness :: InputContent -> Bool
         validateInputWitness input =
@@ -356,8 +417,10 @@ mkMarloweValidator

     -- Tally the deposits in the input.
     collectDeposits :: InputContent -> Val.Value
-    collectDeposits (IDeposit _ _ (Token cur tok) amount) = Val.singleton cur tok amount
-    collectDeposits _                                     = zero
+    collectDeposits (IDeposit _ _ (Token cur tok) amount)
+      | amount > 0    = Val.singleton cur tok amount  -- SCP-5123: Semantically negative deposits
+      | otherwise     = zero                          -- do not remove funds from the script's UTxO.
+    collectDeposits _ = zero

### 2023-03-29 response-to-audit-report.md

     -- Extract the payout to a party.
     payoutByParty :: Payment -> AssocMap.Map Party Val.Value
@@ -374,12 +437,17 @@ mkMarloweValidator
       where
         payoutToTxOut :: (Party, Val.Value) -> Bool
         payoutToTxOut (party, value) = case party of
+            -- [Marlowe-Cardano Specification: "Constraint 15. Sufficient Payment".]
+            -- SCP-5128: Note that the payment to an address may be split into several outputs but the payment to a role must be
+            -- a single output. The flexibily of multiple outputs accommodates wallet-related practicalities such as the change and
+            -- the return of the role token being in separate UTxOs in situations where a contract is also paying to the address
+            -- where that change and that role token are sent.
             Address _ address  -> traceIfFalse "p" $ value `Val.leq` valuePaidToAddress address  -- At least sufficient value paid.
             Role role -> let
                 hsh = findDatumHash' (rolesCurrency, role)
                 addr = Address.scriptHashAddress rolePayoutValidatorHash
                 -- Some output must have the correct value and datum to the role-payout address.
-                in traceIfFalse "r" $ any (checkScriptOutputRelaxed addr hsh value) allOutputs
+                in traceIfFalse "r" $ any (checkScriptOutput Val.geq addr hsh value) allOutputs

     -- The key for the address must have signed.
     txSignedByAddress :: Ledger.Address -> Bool
@@ -402,7 +470,7 @@ marloweValidator :: Scripts.TypedValidator TypedMarloweValidator
 marloweValidator =
   let
     mkUntypedMarloweValidator :: ValidatorHash -> BuiltinData -> BuiltinData -> BuiltinData -> ()
-    mkUntypedMarloweValidator rp = mkUntypedValidator (mkMarloweValidator rp)
+    mkUntypedMarloweValidator rp = Scripts.mkUntypedValidator (mkMarloweValidator rp)

     untypedValidator :: Scripts.Validator
     untypedValidator = mkValidatorScript $
@@ -410,10 +478,20 @@ marloweValidator =
         `PlutusTx.applyCode` PlutusTx.liftCode rolePayoutValidatorHash

     typedValidator :: Scripts.TypedValidator Scripts.Any
-    typedValidator = Scripts.unsafeMkTypedValidator untypedValidator
+    typedValidator = unsafeMkTypedValidator (Scripts.Versioned untypedValidator Scripts.PlutusV2)
   in
     unsafeCoerce typedValidator

+
+marloweValidatorCompiled :: PlutusTx.CompiledCode (ValidatorHash -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> ())
+marloweValidatorCompiled =
+  let
+    mkUntypedMarloweValidator :: ValidatorHash -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> PlutusTx.BuiltinData -> ()
+    mkUntypedMarloweValidator rp = Scripts.mkUntypedValidator (mkMarloweValidator rp)
+  in
+    $$(PlutusTx.compile [|| mkUntypedMarloweValidator ||])
+
+
 -- | The hash of the Marlowe semantics validator.
 marloweValidatorHash :: ValidatorHash
 marloweValidatorHash = Scripts.validatorHash marloweValidator
@@ -432,7 +510,7 @@ alternateMarloweValidator = Scripts.mkTypedValidator
           $$(PlutusTx.compile [|| mkMarloweValidator ||])
             `PlutusTx.applyCode`
               PlutusTx.liftCode rolePayoutValidatorHash
-        mkArgsValidator = mkUntypedValidator @MarloweData @MarloweInput
+        mkArgsValidator = Scripts.mkUntypedValidator @_ @MarloweData @MarloweInput
         compiledArgsValidator =
           $$(PlutusTx.compile [|| mkArgsValidator ||])
```

### 2023-03-29 response-to-audit-report.md

# Response to Audit Report

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO:

@@

- [ ] Add prefatory text and executive summary.
- [ ] Add responses and mitigation commits to Isabelle-related findings.
- [x] Add responses and mitigation commits to Haskell-related findings.
- [ ] Fix display of equations or replace ones that cannot be fixed with ellipses ("...").
- [ ] Replace broken links and cross references, or use elipses ("...").
- [ ] Verify the section numbering is correct.
- [ ] Add table of contents.
- [ ] Proofread.

## Executive Summary

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO: @bwbush will add text here after everything else is written.

@@

## Acknowledgement

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO: @bwbush will add text thanking the audit team.

@@

## Overview of Isabelle Changes

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO: @hrajchert will add text here.

@@

Although this `Eq` instance is not used by the Marlowe validators (so it does not have implications for validator security), the equality test has been fixed because it is a liability for off-chain code and for potential future versions of validators that might perform such an equality test. Commit [84d65a70](https://github.com/input-output-hk/marlowe-cardano/commit/84d65a70c29320fab501ad759bbc71855d1b63fc) fixes this and commit [04805a39](https://github.com/input-output-hk/marlowe-cardano/commit/04805a393c0815fe0f2a1a6d7f76d9867ffe0c14) hardens all of the other `Eq` instances to prevent similar problems re-arising if sum types are augmented in the future.

### 2.1.4 Inaccurate formulation of Money preservation *(Severity: High)*

> **File `specification-v3-rc1.pdf`, Section `3.1 Money preservation`, page *29***
> 
> As the property stands, it is permitted to make deposits in one currency and return payments in a different currency. As long as the sums of the amounts match, the equality is satisfied. Yet it is unlikely that the participants of the contract would agree that money has been preserved.
> 
> Money preservation is a property stated with an equality. The left hand side is the sum of the deposits done by a list of transactions. The right hand side of the equality is the sum of all the payments done in the same list of transactions. Each sum, in turn, is represented as a single integer which aggregates the amounts of the various payments and deposits, irrespective of what currencies correspond to these amounts.

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO: @hrajchert will add text here, since it relates to the Isabelle specification.

@@

## 2.7 Haskell tests

### 2.7.1 More precise failure checks *(Severity: Medium)*

> **File `Spec/Marlowe/Plutus/Specification.hs`, `Various tests`** 
> 
> The tests use the functions `checkSemanticsTransaction` and `checkPayoutTransaction` to verify that various error conditions cause transactions to be rejected. These functions test that a transaction passes or fails, but when it fails, the functions do not consider the error cause. Checking the exact cause is necessary to ensure the transaction is rejected because of the intended reason and not because of some other error condition arising in a particular test case by coincidence.
> 
> The absence of this information makes it easier to accidentally produce a test that is not testing what is intended.

![#f03c15](https://placehold.co/15x15/f03c15/f03c15.png) TODO: @bwbush will add text here.

### 2023-03-29 response-to-audit-report.md

## 2.7 Haskell tests

### 2.7.1 More precise failure checks *(Severity: Medium)*

> **File `Spec/Marlowe/Plutus/Specification.hs`, `Various tests`** 
> 
> The tests use the functions `checkSemanticsTransaction` and `checkPayoutTransaction` to verify that various error conditions cause transactions to be rejected. These functions test that a transaction passes or fails, but when it fails, the functions do not consider the error cause. Checking the exact cause is necessary to ensure the transaction is rejected because of the intended reason and not because of some other error condition arising in a particular test case by coincidence.
> 
> The absence of this information makes it easier to accidentally produce a test that is not testing what is intended.

A future version of the Marlowe test suite for `checkSemanticsTransaction` and `checkPayoutTransaction` will instrumenting Plutus scripts for the Marlowe validators so that the precise cause of the test failure can be verified.
